\begin{thebibliography}{1}

	\bibitem[]{citation1} Adam RC, Yang H, Rockowitz S, Larsen SB, Nikolova M, Oristian DS, Polak L, Kadaja M, Asare A, Zheng D, et al. 2015. Pioneer factors govern super-enhancer dynamics in stem cell plasticity and lineage choice. Nature 521: 366–370. http://dx.doi.org/10.1038/nature14289.
	\bibitem[]{citation2} Aday AW, Zhu LJ, Lakshmanan A, Wang J, Lawson ND. 2011. Identification of cis regulatory features in the embryonic zebrafish genome through large-scale profiling of H3K4me1 and H3K4me3 binding sites. Dev Biol 357: 450–462.
	\bibitem[]{citation3} Agarwal H, Reisser M, Wortmann C, Gebhardt JCM. 2017. Direct Observation of Cell-Cycle-Dependent Interactions between CTCF and Chromatin. Biophys J 112: 2051–2055. http://dx.doi.org/10.1016/j.bpj.2017.04.018.
	\bibitem[]{citation4} Alberts et al. 2007. Molecular Biology of the Cell, 5th ed Garland Science, New York, USA.
	\bibitem[]{citation5} Amaral PP, Leonardi T, Han N, Vire E, Gascoigne DK, Arias-Carrasco R, Buscher M, Zhang A, Pluchino S, Maracaja-Coutinho V, et al. 2016. Genomic positional conservation identifies topological anchor point (tap)RNAs linked to developmental loci. Genome Biol 051052. http://biorxiv.org/lookup/doi/10.1101/051052.
	\bibitem[]{citation6} Andersson R, Gebhard C, Miguel-Escalada I, Hoof I, Bornholdt J, Boyd M, Chen Y, Zhao X, Schmidl C, Suzuki T, et al. 2014. An atlas of active enhancers across human cell types and tissues. Nature 507: 455–461.
	\bibitem[]{citation7} Arnold CD, Gerlach D, Spies D, Matts JA, Sytnikova YA, Pagani M, Lau NC, Stark A. 2014. Quantitative genome-wide enhancer activity maps for five Drosophila species show functional enhancer conservation and turnover during cis-regulatory evolution. Nat Genet 46: 685–692. http://dx.doi.org/10.1038/ng.3009.
	\bibitem[]{citation8} Arnold CD, Gerlach D, Stelzer C, Boryn LM, Rath M, Stark A. 2013. Genome-Wide Quantitative Enhancer Activity Maps Identified by STARR-seq. Science (80- ) 339: 1074–1077. http://www.sciencemag.org/cgi/doi/10.1126/science.1232542.
	\bibitem[]{citation9} Auer TO, Duroure K, Cian A De, Concordet J, Bene F Del. 2014. Highly efficient CRISPR / Cas9-mediated knock-in in zebrafish by homology-independent DNA repair. Genome Res 24: 142–153.
	\bibitem[]{citation10} Azuara V, Perry P, Sauer S, Spivakov M, Jørgensen HF, John RM, Gouti M, Casanova M, Warnes G, Merkenschlager M, et al. 2006. Chromatin signatures of pluripotent cell lines. Nat Cell Biol 8: 532–538.
	\bibitem[]{citation11} Bahr C, von Paleske L, Uslu V V, Remeseiro S, Takayama N, Ng SW, Murison A, Langenfeld K, Petretich M, Scognamiglio R, et al. 2018. A Myc enhancer cluster regulates normal and leukaemic haematopoietic stem cell hierarchies The transcription factor Myc is essential for the regulation of haematopoietic stem cells and progenitors and has a critical function in haematopoietic malignancies. Nat Publ Gr 553: 515–520. http://dx.doi.org/10.1038/nature25193.
	\bibitem[]{citation12} Banerji J, Rusconi S, Schaffner W. 1981. Expression of a $\beta$-globin gene is enhanced by remote SV40 DNA sequences. Cell. 27: 299-308.
	\bibitem[]{citation13} Banerji J, Olson L, Schaffner W. 1983. A lymphocyte-specific cellular enhancer is located downstream of the joining region in immunoglobulin heavy chain genes. Cell. 33: 729-40.
	\bibitem[]{citation14} Barakat TS, Halbritter F, Zhang M, Rendeiro AF, Perenthaler E, Bock C, Chambers I. 2018. Functional Dissection of the Enhancer Repertoire in Human Embryonic Stem Cells. Cell Stem Cell 23: 276–288.e8. https://linkinghub.elsevier.com/retrieve/pii/S1934590918302960.
	\bibitem[]{citation15} Barski A, Cuddapah S, Cui K, Roh TY, Schones DE, Wang Z, Wei G, Chepelev I, Zhao K. 2007. High-Resolution Profiling of Histone Methylations in the Human Genome. Cell 129: 823–837.
	\bibitem[]{citation16} Battulin N, Fishman VS, Mazur AM, Pomaznoy M, Khabarova AA, Afonnikov DA, Prokhortchouk EB, Serov OL. 2015. Comparison of the three-dimensional organization of sperm and fibroblast genomes using the Hi-C approach. Genome Biol 16: 77. http://dx.doi.org/10.1186/s13059-015-0642-0.
	\bibitem[]{citation17} Baudement M, Cournac A, Court F, Seveno M, Parrinello H, Reynes C, Sabatier R, Bouschet T, Yi Z, Sallis S, et al. 2018. High-salt – recovered sequences are associated with the active chromosomal compartment and with large ribonucleoprotein complexes including nuclear bodies. 1–14.
	\bibitem[]{citation18} Beagrie RA, Scialdone A, Schueler M, Kraemer DCA, Chotalia M, Xie SQ, Barbieri M, De Santiago I, Lavitas LM, Branco MR, et al. 2017. Complex multi-enhancer contacts captured by genome architecture mapping. Nature 543: 519–524. http://dx.doi.org/10.1038/nature21411.
	\bibitem[]{citation19} Bejerano G, Pheasant M, Makunin I, Stephen S, Kent WJ, Mattick JS, Haussler D. 2004. Ultraconserved elements in the human genome. Science 304: 1321–5. http://www.sciencemag.org/cgi/doi/10.1126/science.1098119.
	\bibitem[]{citation20} Bernstein BE, Mikkelsen TS, Xie X, Kamal M, Huebert DJ, Cuff J, Fry B, Meissner A, Wernig M, Plath K, et al. 2006. A Bivalent Chromatin Structure Marks Key Developmental Genes in Embryonic Stem Cells. Cell 125: 315–326.
	\bibitem[]{citation21} Blinka S, Reimer MH, Pulakanti K, Rao S. 2016. Super-Enhancers at the Nanog Locus Differentially Regulate Neighboring Pluripotency-Associated Genes. Cell Rep 17: 19–28. http://dx.doi.org/10.1016/j.celrep.2016.09.002.
	\bibitem[]{citation22} Bogdanović O, Fernandez-Miñán A, Tena JJ, De La Calle-Mustienes E, Hidalgo C, Van Kruysbergen I, Van Heeringen SJ, Veenstra GJC, Gómez-Skarmeta JL. 2012. Dynamics of enhancer chromatin signatures mark the transition from pluripotency to cell specification during embryogenesis. Genome Res 22: 2043–2053.
	\bibitem[]{citation23} Bogdanović O, Smits AH, De La Calle Mustienes E, Tena JJ, Ford E, Williams R, Senanayake U, Schultz MD, Hontelez S, Van Kruijsbergen I, et al. 2016. Active DNA demethylation at enhancers during the vertebrate phylotypic period. Nat Genet 48: 417–426.
	\bibitem[]{citation24} Bonev B, Mendelson Cohen N, Szabo Q, Fritsch L, Papadopoulos GL, Lubling Y, Xu X, Lv X, Hugnot JP, Tanay A, et al. 2017. Multiscale 3D Genome Rewiring during Mouse Neural Development. Cell 171: 557–572.e24. https://doi.org/10.1016/j.cell.2017.09.043.
	\bibitem[]{citation25} Calo E, Wysocka J. 2013. Modification of Enhancer Chromatin: What, How, and Why? Mol Cell 49: 825–837. http://dx.doi.org/10.1016/j.molcel.2013.01.038.
	\bibitem[]{citation26} Carelli FN, Liechti A, Halbert J, Warnefors M, Kaessmann H. 2018. Repurposing of promoters and enhancers during mammalian evolution. Nat Commun 9: 4066. http://www.ncbi.nlm.nih.gov/pubmed/30287902.
	\bibitem[]{citation27} Carmona-Aldana F, Zampedri C, Suaste-Olmos F, Murillo-de-Ozores A, Guerrero G, Arzate-Mejía R, Maldonado E, Navarro RE, Chimal-Monroy J, Recillas-Targa F. 2018. CTCF knockout reveals an essential role for this protein during the zebrafish development. Mech Dev 1–9. https://doi.org/10.1016/j.mod.2018.04.006.
	\bibitem[]{citation28} Cho SW, Xu J, Sun R, Mumbach MR, Carter AC, Chen YG, Yost KE, Kim J, He J, Nevins SA, et al. 2018a. Promoter of lncRNA Gene PVT1 Is a Tumor-Suppressor DNA Boundary Element. Cell 173: 1398–1412.e22. http://linkinghub.elsevier.com/retrieve/pii/S0092867418304008.
	\bibitem[]{citation29} Cho W-K, Spille J-H, Hecht M, Lee C, Li C, Grube V, Cisse II. 2018b. Mediator and RNA polymerase II clusters associate in transcription-dependent condensates. Science (80- ) 361: 412–415. www.sciencemag.org/cgi/content/full/science.aar4199/DC1.
	\bibitem[]{citation30} Clarke SL, VanderMeer JE, Wenger AM, Schaar BT, Ahituv N, Bejerano G. 2012. Human Developmental Enhancers Conserved between Deuterostomes and Protostomes ed. J. Brosius. PLoS Genet 8: e1002852. http://dx.plos.org/10.1371/journal.pgen.1002852.
	\bibitem[]{citation31} Core LJ, Martins AL, Danko CG, Waters CT, Siepel A, Lis JT. 2014. Analysis of nascent RNA identifies a unified architecture of initiation regions at mammalian promoters and enhancers. Nat Genet 46: 1311–1320.
	\bibitem[]{citation32} Creyghton MP, Cheng AW, Welstead GG, Kooistra T, Carey BW, Steine EJ, Hanna J, Lodato MA, Frampton GM, Sharp PA, et al. 2010. Histone H3K27ac separates active from poised enhancers and predicts developmental state. Proc Natl Acad Sci 107: 21931–21936. http://www.pnas.org/cgi/doi/10.1073/pnas.1016071107.
	\bibitem[]{citation33} Criscione SW, De Cecco M, Siranosian B, Zhang Y, Kreiling JA, Sedivy JM, Neretti N. 2016. Reorganization of chromosome architecture in replicative cellular senescence. Sci Adv 2: e1500882. http://advances.sciencemag.org/lookup/doi/10.1126/sciadv.1500882.
	\bibitem[]{citation34} Da Rocha ST, Heard E. 2017. Novel players in X inactivation: Insights into Xist-mediated gene silencing and chromosome conformation. Nat Struct Mol Biol 24: 197–204. http://dx.doi.org/10.1038/nsmb.3370.
	\bibitem[]{citation35} Danko CG, Hyland SL, Core LJ, Martins AL, Waters CT, Lee HW, Cheung VG, Kraus WL, Lis JT, Siepel A. 2015. Identification of active transcriptional regulatory elements from GRO-seq data. Nat Methods 12: 433–438.
	\bibitem[]{citation36} Dao LTM, Galindo-Albarrán AO, Castro-Mondragon JA, Andrieu-Soler C, Medina-Rivera A, Souaid C, Charbonnier G, Griffon A, Vanhille L, Stephen T, et al. 2017. Genome-wide characterization of mammalian promoters with distal enhancer functions. Nat Genet 49: 1073–1081. http://dx.doi.org/10.1038/ng.3884.
	\bibitem[]{citation37} de Wit E, Vos ESM, Holwerda SJB, Valdes-Quezada C, Verstegen MJAM, Teunissen H, Splinter E, Wijchers PJ, Krijger PHL, de Laat W. 2015. CTCF Binding Polarity Determines Chromatin Looping. Mol Cell 60: 676–684. http://dx.doi.org/10.1016/j.molcel.2015.09.023.
	\bibitem[]{citation38} Deaton A, Bird A. 2011. CpG islands and the regulation of transcription. Genes Dev 25: 1010–1022. http://genesdev.cshlp.org/content/25/10/1010.short.
	\bibitem[]{citation39} Decker KB, Hinton DM. 2013. Transcription Regulation at the Core: Similarities Among Bacterial, Archaeal, and Eukaryotic RNA Polymerases. Annu Rev Microbiol 67: 113–139. http://www.annualreviews.org/doi/10.1146/annurev-micro-092412-155756.
	\bibitem[]{citation40} Dekker J. 2016. Mapping the 3D genome: Aiming for consilience. Nat Rev Mol Cell Biol 17: 741–742. http://dx.doi.org/10.1038/nrm.2016.151.
	\bibitem[]{citation41} Dekker J, Rippe K, Dekker M, Kleckner N. 2002. Capturing chromosome conformation. Science 295: 1306–11. http://www.ncbi.nlm.nih.gov/pubmed/11847345.
	\bibitem[]{citation42} Delgado-Olguín P, Brand-Arzamendi K, Scott IC, Jungblut B, Stainier DY, Bruneau BG, Recillas-Targa F. 2011. CTCF promotes muscle differentiation by modulating the activity of myogenic regulatory factors. J Biol Chem 286: 12483–12494.
	\bibitem[]{citation43} Denker A, De Laat W. 2016. The second decade of 3C technologies: Detailed insights into nuclear organization. Genes Dev 30: 1357–1382.
	\bibitem[]{citation44} Dixon JR, Jung I, Selvaraj S, Shen Y, Antosiewicz-Bourget JE, Lee AY, Ye Z, Kim A, Rajagopal N, Xie W, et al. 2015. Chromatin architecture reorganization during stem cell differentiation. Nature 518: 331–336. http://dx.doi.org/10.1038/nature14222.
	\bibitem[]{citation45} Dixon JR, Selvaraj S, Yue F, Kim A, Li Y, Shen Y, Hu M, Liu JS, Ren B. 2012. Topological domains in mammalian genomes identified by analysis of chromatin interactions. Nature 485: 376–380. http://dx.doi.org/10.1038/nature11082.
	\bibitem[]{citation46} Dowen JM, Fan ZP, Hnisz D, Ren G, Abraham BJ, Zhang LN, Weintraub AS, Schuijers J, Lee TI, Zhao K, et al. 2014. Control of cell identity genes occurs in insulated neighborhoods in mammalian chromosomes. Cell 159: 374–387. http://dx.doi.org/10.1016/j.cell.2014.09.030.
	\bibitem[]{citation47} Dunham I, Kundaje A, Aldred SF, Collins PJ, Davis CA, Doyle F, Epstein CB, Frietze S, Harrow J, Kaul R, et al. 2012. An integrated encyclopedia of DNA elements in the human genome. Nature 489: 57–74.
	\bibitem[]{citation48} Engel C, Neyer S, Cramer P. 2018. Distinct Mechanisms of Transcription Initiation by RNA Polymerases I and II. Annu Rev Biophys 47: 425–446. https://doi.org/10.1146/annurev-biophys-.
	\bibitem[]{citation49} Farrell JA, Wang Y, Riesenfeld SJ, Shekhar K, Regev A, Schier AF. 2018. Single-cell reconstruction of developmental trajectories during zebrafish embryogenesis. Science 360: 1–15. http://www.ncbi.nlm.nih.gov/pubmed/29700225.
	\bibitem[]{citation50} Fedoriw AM, Stein P, Svoboda P, Schultz RM, Bartolomei MS. 2004. Transgenic RNAi reveals essential function for CTCF in H19 gene imprinting. Science 303: 238–40. http://www.ncbi.nlm.nih.gov/pubmed/14716017.
	\bibitem[]{citation51} Filippova GN, Fagerlie S, Klenova EM, Myers C, Dehner Y, Goodwin G, Neiman PE, Collins SJ, Lobanenkov V V. 1996. An exceptionally conserved transcriptional repressor, CTCF, employs different combinations of zinc fingers to bind diverged promoter sequences of avian and mammalian c-myc oncogenes. Mol Cell Biol 16: 2802–13. http://mcb.asm.org/lookup/doi/10.1128/MCB.16.6.2802.
	\bibitem[]{citation52} Flyamer IM, Gassler J, Imakaev M, Brandão HB, Ulianov S V., Abdennur N, Razin S V., Mirny LA, Tachibana-Konwalski K. 2017. Single-nucleus Hi-C reveals unique chromatin reorganization at oocyte-to-zygote transition. Nature 544: 110–114. http://dx.doi.org/10.1038/nature21711.
	\bibitem[]{citation53} Forrest ARR, Kawaji H, Rehli M, Baillie JK, De Hoon MJL, Haberle V, Lassmann T, Kulakovskiy I V., Lizio M, Itoh M, et al. 2014. A promoter-level mammalian expression atlas. Nature 507: 462–470. http://dx.doi.org/10.1038/nature13182.
	\bibitem[]{citation54} Franke M, Ibrahim DM, Andrey G, Schwarzer W, Heinrich V, Schöpflin R, Kraft K, Kempfer R, Jerković I, Chan WL, et al. 2016. Formation of new chromatin domains determines pathogenicity of genomic duplications. Nature 538: 265–269. http://dx.doi.org/10.1038/nature19800.
	\bibitem[]{citation55} Fudenberg G, Imakaev M. 2017. FISH-ing for captured contacts: Towards reconciling FISH and 3C. Nat Methods 14: 673–678. http://dx.doi.org/10.1038/nmeth.4329.
	\bibitem[]{citation56} Fudenberg G, Imakaev M, Lu C, Goloborodko A, Abdennur N, Mirny LA. 2016. Formation of Chromosomal Domains by Loop Extrusion. Cell Rep 15: 2038–2049.
	\bibitem[]{citation57} Fukaya T, Lim B, Levine M. 2016. Enhancer Control of Transcriptional Bursting. Cell 166: 358–368. http://dx.doi.org/10.1016/j.cell.2016.05.025.
	\bibitem[]{citation58} Gassler J, Brandão HB, Imakaev M, Flyamer IM, Ladstätter S, Bickmore WA, Peters J, Mirny LA, Tachibana K. 2017. A mechanism of cohesin - dependent loop extrusion organizes zygotic genome architecture. EMBO J 36: e201798083. http://emboj.embopress.org/lookup/doi/10.15252/embj.201798083.
	\bibitem[]{citation59} Gershenzon NI, Ioshikhes IP. 2005. Synergy of human Pol II core promoter elements revealed by statistical sequence analysis. Bioinformatics 21: 1295–300. http://www.ncbi.nlm.nih.gov/pubmed/15572469.
	\bibitem[]{citation60} Giorgetti L, Heard E. 2016. Closing the loop: 3C versus DNA FISH. Genome Biol 17: 215. http://dx.doi.org/10.1186/s13059-016-1081-2.
	\bibitem[]{citation61} Giorgetti L, Lajoie BR, Carter AC, Attia M, Zhan Y, Xu J, Chen CJ, Kaplan N, Chang HY, Heard E, et al. 2016. Structural organization of the inactive X chromosome in the mouse. Nature 535: 575–579.
	\bibitem[]{citation62} Gómez-Marín C, Tena JJ, Acemel RD, López-Mayorga M, Naranjo S, de la Calle-Mustienes E, Maeso I, Beccari L, Aneas I, Vielmas E, et al. 2015. Evolutionary comparison reveals that diverging CTCF sites are signatures of ancestral topological associating domains borders. Proc Natl Acad Sci 112: 7542–7547. http://www.pnas.org/lookup/doi/10.1073/pnas.1505463112.
	\bibitem[]{citation63} Groff AF, Sanchez-Gomez DB, Soruco MML, Gerhardinger C, Barutcu AR, Li E, Elcavage L, Plana O, Sanchez L V., Lee JC, et al. 2016. In Vivo Characterization of Linc-p21 Reveals Functional cis -Regulatory DNA Elements. Cell Rep 16: 2178–2186. http://dx.doi.org/10.1016/j.celrep.2016.07.050.
	\bibitem[]{citation64} Guenther MG, Levine SS, Boyer LA, Jaenisch R, Young RA. 2007. A Chromatin Landmark and Transcription Initiation at Most Promoters in Human Cells. Cell 130: 77–88.
	\bibitem[]{citation65} Guo Y, Xu Q, Canzio D, Shou J, Li J, Gorkin DU, Jung I, Wu H, Zhai Y, Tang Y, et al. 2015. CRISPR Inversion of CTCF Sites Alters Genome Topology and Enhancer/Promoter Function. Cell 162: 900–910. http://dx.doi.org/10.1016/j.cell.2015.07.038.
	\bibitem[]{citation66} Gurdon JB. 1968. Transplanted nuclei and cell differentiation. Sci Am. 219: 24-35.
	\bibitem[]{citation67} Haarhuis JHI, van der Weide RH, Blomen VA, Yáñez-Cuna JO, Amendola M, van Ruiten MS, Krijger PHL, Teunissen H, Medema RH, van Steensel B, et al. 2017. The Cohesin Release Factor WAPL Restricts Chromatin Loop Extension. Cell 169: 693–707.e14.
	\bibitem[]{citation68} Haberle V, Stark A. 2018. Eukaryotic core promoters and the functional basis of transcription initiation. Nat Rev Mol Cell Biol 19: 621–637. http://dx.doi.org/10.1038/s41580-018-0028-8.
	\bibitem[]{citation69} Hacisuleyman E, Goff LA, Trapnell C, Williams A, Henao-Mejia J, Sun L, McClanahan P, Hendrickson DG, Sauvageau M, Kelley DR, et al. 2014. Topological organization of multichromosomal regions by the long intergenic noncoding RNA Firre. Nat Struct Mol Biol 21: 198–206.
	\bibitem[]{citation70} Hantsche M, Cramer P. 2017. ScienceDirect Conserved RNA polymerase II initiation complex structure. Curr Opin Struct Biol 47: 17–22. http://dx.doi.org/10.1016/j.sbi.2017.03.013.
	\bibitem[]{citation71} Hare EE, Peterson BK, Iyer VN, Meier R, Eisen MB. 2008. Sepsid even-skipped enhancers are functionally conserved in Drosophila despite lack of sequence conservation. PLoS Genet 4: e1000106. http://www.ncbi.nlm.nih.gov/pubmed/18584029.
	\bibitem[]{citation72} Harmston N, Ing-Simmons E, Tan G, Perry M, Merkenschlager M, Lenhard B. 2017. Topologically associating domains are ancient features that coincide with Metazoan clusters of extreme noncoding conservation. Nat Commun 8: 441. http://dx.doi.org/10.1038/s41467-017-00524-5.
	\bibitem[]{citation73} Hay D, Hughes JR, Babbs C, Davies JOJ, Graham BJ, Hanssen LLP, Kassouf MT, Oudelaar AM, Sharpe JA, Suciu MC, et al. 2016. Genetic dissection of the $\alpha$-globin super-enhancer in vivo. Nat Genet 48: 895–903. http://dx.doi.org/10.1038/ng.3605.
	\bibitem[]{citation74} Heger P, Marin B, Bartkuhn M, Schierenberg E, Wiehe T. 2012. The chromatin insulator CTCF and the emergence of metazoan diversity. Proc Natl Acad Sci 109: 17507–17512. http://www.pnas.org/cgi/doi/10.1073/pnas.1111941109.
	\bibitem[]{citation75} Heintzman ND, Hon GC, Hawkins RD, Kheradpour P, Stark A, Harp LF, Ye Z, Lee LK, Stuart RK, Ching CW, et al. 2009. Histone modifications at human enhancers reflect global cell-type-specific gene expression. Nature 459: 108–112. http://dx.doi.org/10.1038/nature07829.
	\bibitem[]{citation76} Heinz S, Texari L, Hayes MGB, Urbanowski M, Chang MW, Givarkes N, Rialdi A, White KM, Albrecht RA, Pache L, et al. 2018. Transcription Elongation Can Affect Genome 3D Structure. Cell 174: 1522–1536.e22. https://linkinghub.elsevier.com/retrieve/pii/S0092867418309759.
	\bibitem[]{citation77} Hnisz D, Abraham BJ, Lee TI, Lau A, Saint-André V, Sigova AA, Hoke HA, Young RA. 2013. Super-Enhancers in the Control of Cell Identity and Disease. Cell 155: 934–947. https://linkinghub.elsevier.com/retrieve/pii/S0092867413012270.
	\bibitem[]{citation78} Hnisz D, Day DS, Young RA. 2016. Insulated Neighborhoods: Structural and Functional Units of Mammalian Gene Control. Cell 167: 1188–1200. http://dx.doi.org/10.1016/j.cell.2016.10.024.
	\bibitem[]{citation79} Hnisz D, Schuijers J, Lin CY, Weintraub AS, Abraham BJ, Lee TI, Bradner JE, Young RA. 2015. Convergence of Developmental and Oncogenic Signaling Pathways at Transcriptional Super-Enhancers. Mol Cell 58: 362–370. http://dx.doi.org/10.1016/j.molcel.2015.02.014.
	\bibitem[]{citation80} Hnisz D, Shrinivas K, Young RA, Chakraborty AK, Sharp PA. 2017. A Phase Separation Model for Transcriptional Control. Cell 169: 13–23. http://dx.doi.org/10.1016/j.cell.2017.02.007.
	\bibitem[]{citation81} Hoffman EA, Frey BL, Smith LM, Auble DT. 2015. Formaldehyde crosslinking: A tool for the study of chromatin complexes. J Biol Chem 290: 26404–26411.
	\bibitem[]{citation82} Howe K, Clark MD, Torroja CF, Torrance J, Berthelot C, Muffato M, Collins JE, Humphray S, McLaren K, Matthews L, et al. 2013. The zebrafish reference genome sequence and its relationship to the human genome. Nature 496: 498–503.
	\bibitem[]{citation83} Hug CB, Grimaldi AG, Kruse K, Vaquerizas JM. 2017. Chromatin Architecture Emerges during Zygotic Genome Activation Independent of Transcription. Cell 169: 216–228.e19. http://dx.doi.org/10.1016/j.cell.2017.03.024.
	\bibitem[]{citation84} Hwang WY, Fu Y, Reyon D, Maeder ML, Tsai SQ, Sander JD, Peterson RT, Yeh JRJ, Joung JK. 2013. Efficient genome editing in zebrafish using a CRISPR-Cas system. Nat Biotechnol 31: 227–229. http://dx.doi.org/10.1038/nbt.2501.
	\bibitem[]{citation85} Ibn-Salem J, Köhler S, Love MI, Chung H-R, Huang N, Hurles ME, Haendel M, Washington NL, Smedley D, Mungall CJ, et al. 2014. Deletions of chromosomal regulatory boundaries are associated with congenital disease. Genome Biol 15: 423. http://genomebiology.biomedcentral.com/articles/10.1186/s13059-014-0423-1.
	\bibitem[]{citation86} Imakaev M, Fudenberg G, McCord RP, Naumova N, Goloborodko A, Lajoie BR, Dekker J, Mirny LA. 2012. Iterative correction of Hi-C data reveals hallmarks of chromosome organization. Nat Methods 9: 999–1003.
	\bibitem[]{citation87} Jacob F, Monod J. 1961. Genetic regulatory mechanisms in the synthesis of proteins. J Mol Biol. 3: 318-56.
	\bibitem[]{citation88} Jeronimo C, Robert F. 2017. The Mediator Complex: At the Nexus of RNA Polymerase II Transcription. Trends Cell Biol 27: 765–783. http://dx.doi.org/10.1016/j.tcb.2017.07.001.
	\bibitem[]{citation89} Ji X, Dadon DB, Powell BE, Fan ZP, Borges-Rivera D, Shachar S, Weintraub AS, Hnisz D, Pegoraro G, Lee TI, et al. 2016. 3D Chromosome Regulatory Landscape of Human Pluripotent Cells. Cell Stem Cell 18: 262–275. http://dx.doi.org/10.1016/j.stem.2015.11.007.
	\bibitem[]{citation90} Jin C, Zang C, Wei G, Cui K, Peng W, Zhao K, Felsenfeld G. 2009. H3.3/H2A.Z double variant-containing nucleosomes mark “nucleosome-free regions” of active promoters and other regulatory regions. Nat Genet 41: 941–945. http://dx.doi.org/10.1038/ng.409.
	\bibitem[]{citation91} Kaaij LJT, van der Weide RH, Ketting RF, de Wit E. 2018. Systemic Loss and Gain of Chromatin Architecture throughout Zebrafish Development. Cell Rep 24: 1–10.e4. https://linkinghub.elsevier.com/retrieve/pii/S2211124718308982.
	\bibitem[]{citation92} Kagey MH, Newman JJ, Bilodeau S, Zhan Y, Orlando DA, Berkum NL Van, Ebmeier CC, Goossens J, Rahl PB, Levine SS, et al. 2010. Mediator and cohesin connect gene expression and chromatin architecture. Nature 467: 430–435. http://dx.doi.org/10.1038/nature09380.
	\bibitem[]{citation93} Kang J, Hu J, Karra R, Dickson AL, Tornini VA, Nachtrab G, Gemberling M, Goldman JA, Black BL, Poss KD. 2016. Modulation of tissue repair by regeneration enhancer elements. Nature 532: 201–206. http://dx.doi.org/10.1038/nature17644.
	\bibitem[]{citation94} Kaufman CK, Mosimann C, Fan ZP en., Yang S, Thomas AJ, Ablain J, Tan JL, Fogley RD, van Rooijen E, Hagedorn EJ, et al. 2016. A zebrafish melanoma model reveals emergence of neural crest identity during melanoma initiation. Science (80- ) 351: aad2197-aad2197. http://www.sciencemag.org/cgi/doi/10.1126/science.aad2197.
	\bibitem[]{citation95} Ke Y, Xu Y, Chen X, Feng S, Liu Z, Sun Y, Yao X, Li F, Zhu W, Gao L, et al. 2017. 3D Chromatin Structures of Mature Gametes and Structural Reprogramming during Mammalian Embryogenesis. Cell 170: 367–381.e20. http://dx.doi.org/10.1016/j.cell.2017.06.029.
	\bibitem[]{citation96} Kieffer-Kwon KR, Tang Z, Mathe E, Qian J, Sung MH, Li G, Resch W, Baek S, Pruett N, Grøntved L, et al. 2013. Interactome maps of mouse gene regulatory domains reveal basic principles of transcriptional regulation. Cell 155: 1507–1520. http://dx.doi.org/10.1016/j.cell.2013.11.039.
	\bibitem[]{citation97} Kim TK, Hemberg M, Gray JM, Costa AM, Bear DM, Wu J, Harmin DA, Laptewicz M, Barbara-Haley K, Kuersten S, et al. 2010. Widespread transcription at neuronal activity-regulated enhancers. Nature 465: 182–187. http://dx.doi.org/10.1038/nature09033.
	\bibitem[]{citation98} Kok FO, Shin M, Ni CW, Gupta A, Grosse AS, vanImpel A, Kirchmaier BC, Peterson-Maduro J, Kourkoulis G, Male I, et al. 2015. Reverse genetic screening reveals poor correlation between morpholino-induced and mutant phenotypes in zebrafish. Dev Cell 32: 97–108. http://dx.doi.org/10.1016/j.devcel.2014.11.018.
	\bibitem[]{citation99} Krefting J, Andrade-Navarro MA, Ibn-Salem J. 2018. Evolutionary stability of topologically associating domains is associated with conserved gene regulation. BMC Biol 16: 87. https://bmcbiol.biomedcentral.com/articles/10.1186/s12915-018-0556-x.
	\bibitem[]{citation100} Lazar---Stefanita L, Scolari VF, Mercy G, Muller H, Guérin TM, Thierry A, Mozziconacci J, Koszul R. 2017. Cohesins and condensins orchestrate the 4D dynamics of yeast chromosomes during the cell cycle. EMBO J 36: e201797342. http://emboj.embopress.org/lookup/doi/10.15252/embj.201797342.
	\bibitem[]{citation101} Lee HJ, Lowdon RF, Maricque B, Zhang B, Stevens M, Li D, Johnson SL, Wang T. 2015. Developmental enhancers revealed by extensive DNA methylome maps of zebrafish early embryos. Nat Commun 6: 6315. http://www.nature.com/articles/ncomms7315.
	\bibitem[]{citation102} Levine M, Cattoglio C, Tjian R. 2014. Looping Back to Leap Forward: Transcription Enters a New Era. Cell 157: 13–25. http://dx.doi.org/10.1016/j.cell.2014.02.009.
	\bibitem[]{citation103} Lieberman-Aiden E, van Berkum NL, Williams L, Imakaev M, Ragoczy T, Telling A, Amit I, Lajoie BR, Sabo PJ, Dorschner MO, et al. 2009. Comprehensive Mapping of Long-Range Interactions Reveals Folding Principles of the Human Genome. Science (80- ) 326: 289–293. http://www.sciencemag.org/cgi/doi/10.1126/science.1181369.
	\bibitem[]{citation104} Lin CY, Erkek S, Tong Y, Yin L, Federation AJ, Zapatka M, Haldipur P, Kawauchi D, Risch T, Warnatz HJ, et al. 2016. Active medulloblastoma enhancers reveal subgroup-specific cellular origins. Nature 530: 57–62. http://dx.doi.org/10.1038/nature16546.
	\bibitem[]{citation105} Long HK, Prescott SL, Wysocka J. 2016. Review Ever-Changing Landscapes: Transcriptional Enhancers in Development and Evolution. Cell 167: 1170–1187. http://dx.doi.org/10.1016/j.cell.2016.09.018.
	\bibitem[]{citation106} Lovén J, Hoke HA, Lin CY, Lau A, Orlando DA, Vakoc CR, Bradner JE, Lee TI, Young RA. 2013. Selective inhibition of tumor oncogenes by disruption of super-enhancers. Cell 153: 320–334.
	\bibitem[]{citation107} Luo Z, Gao X, Lin C, Smith ER, Marshall SA, Swanson SK, Florens L, Washburn MP, Shilatifard A. 2015. Zic2 is an enhancer-binding factor required for embryonic stem cell specification. Mol Cell 57: 685–694. http://dx.doi.org/10.1016/j.molcel.2015.01.007.
	\bibitem[]{citation108} Lupiáñez DG, Kraft K, Heinrich V, Krawitz P, Brancati F, Klopocki E, Horn D, Kayserili H, Opitz JM, Laxova R, et al. 2015. Disruptions of topological chromatin domains cause pathogenic rewiring of gene-enhancer interactions. Cell 161: 1012–1025.
	\bibitem[]{citation109} Ma W, Ay F, Lee C, Gulsoy G, Deng X, Cook S, Hesson J, Cavanaugh C, Ware CB, Krumm A, et al. 2014. Fine-scale chromatin interaction maps reveal the cis-regulatory landscape of human lincRNA genes. Nat Methods 12: 71–78.
	\bibitem[]{citation110} Maass PG, Barutcu AR, Rinn JL. 2018a. Interchromosomal interactions: A genomic love story of kissing chromosomes. J Cell Biol jcb.201806052. http://www.jcb.org/lookup/doi/10.1083/jcb.201806052.
	\bibitem[]{citation111} Maass PG, Barutcu AR, Weiner CL, Rinn JL. 2018b. Inter-chromosomal Contact Properties in Live-Cell Imaging and in Hi-C. Mol Cell 69: 1039–1045.e3. http://linkinghub.elsevier.com/retrieve/pii/S1097276518301059.
	\bibitem[]{citation112} Mansbridge J. 1998. Skin substitutes to enhance wound healing. Expert Opin Investig Drugs 7: 803–809. http://linkinghub.elsevier.com/retrieve/pii/0092867483900156.
	\bibitem[]{citation113} Mansour MR, Abraham BJ, Anders L, Berezovskaya A, Gutierrez A, Durbin AD, Etchin J, Lawton L, Sallan SE, Silverman LB, et al. 2014. An oncogenic super-enhancer formed through somatic mutation of a noncoding intergenic element. Science (80- ) 346: 1373–1377. http://www.sciencemag.org/cgi/doi/10.1126/science.1259037.
	\bibitem[]{citation114} Marchese FP, Raimondi I, Huarte M. 2017. The multidimensional mechanisms of long noncoding RNA function. Genome Biol 18: 1–13.
	\bibitem[]{citation115} Market E, Papavasiliou FN. 2003. V(D)J recombination and the evolution of the adaptive immune system. PLoS Biol 1: 24–27.
	\bibitem[]{citation116} Marsman J, O’Neill AC, Kao BRY, Rhodes JM, Meier M, Antony J, Mönnich M, Horsfield JA. 2014. Cohesin and CTCF differentially regulate spatiotemporal runx1 expression during zebrafish development. Biochim Biophys Acta - Gene Regul Mech 1839: 50–61.
	\bibitem[]{citation117} Mavrich TN, Jiang C, Ioshikhes IP, Li X, Venters BJ, Zanton SJ, Tomsho LP, Qi J, Glaser RL, Schuster SC, et al. 2008. Nucleosome organization in the Drosophila genome. Nature 453: 358–362.
	\bibitem[]{citation118} Mayer A, Landry HM, Churchman LS. 2017. Pause \& go: from the discovery of RNA polymerase pausing to its functional implications. Curr Opin Cell Biol 46: 72–80. http://dx.doi.org/10.1016/j.ceb.2017.03.002.
	\bibitem[]{citation119} Meier M, Grant J, Dowdle A, Thomas A, Gerton J, Collas P, O’Sullivan JM, Horsfield JA. 2018. Cohesin facilitates zygotic genome activation in zebrafish. Development 145: dev156521. http://dev.biologists.org/lookup/doi/10.1242/dev.156521.
	\bibitem[]{citation120} Meng FL, Du Z, Federation A, Hu J, Wang Q, Kieffer-Kwon KR, Meyers RM, Amor C, Wasserman CR, Neuberg D, et al. 2014. Convergent transcription at intragenic super-enhancers targets AID-initiated genomic instability. Cell 159: 1538–1548. http://dx.doi.org/10.1016/j.cell.2014.11.014.
	\bibitem[]{citation121} Minzel W, Venkatachalam A, Fink A, Hung E, Brachya G, Burstain I, Shaham M, Rivlin A, Omer I, Zinger A, et al. 2018. Small Molecules Co - targeting CKI$\alpha$ and the Transcriptional Kinases CDK7/9 Control AML in Preclinical Models. Cell 175: 171–185.e25. https://doi.org/10.1016/j.cell.2018.07.045.
	\bibitem[]{citation122} Moorthy SD, Davidson S, Shchuka VM, Singh G, Malek-Gilani N, Langroudi L, Martchenko A, So V, Macpherson NN, Mitchell JA. 2017. Enhancers and super-enhancers have an equivalent regulatory role in embryonic stem cells through regulation of single or multiple genes. Genome Res 27: 246–258. http://genome.cshlp.org/lookup/doi/10.1101/gr.210930.116.
	\bibitem[]{citation123} Mumbach MR, Rubin AJ, Flynn RA, Dai C, Khavari PA, Greenleaf WJ, Chang HY. 2016. HiChIP: Efficient and sensitive analysis of protein-directed genome architecture. Nat Methods 13: 919–922.
	\bibitem[]{citation124} Nagano T, Lubling Y, Várnai C, Dudley C, Leung W, Baran Y, Mendelson Cohen N, Wingett S, Fraser P, Tanay A. 2017. Cell-cycle dynamics of chromosomal organization at single-cell resolution. Nature 547: 61–67. http://dx.doi.org/10.1038/nature23001.
	\bibitem[]{citation125} Naumova N, Imakaev M, Fudenberg G, Zhan Y, Lajoie BR, Mirny L a, Dekker J. 2013. Organization of the Mitotic Chromosome. Science (80- ) 342: 948–953. http://www.sciencemag.org/cgi/doi/10.1126/science.1236083.
	\bibitem[]{citation126} Nelson AC, Cutty SJ, Gasiunas SN, Deplae I, Stemple DL, Wardle FC. 2017. In Vivo Regulation of the Zebrafish Endoderm Progenitor Niche by T-Box Transcription Factors. Cell Rep 19: 2782–2795. http://dx.doi.org/10.1016/j.celrep.2017.06.011.
	\bibitem[]{citation127} Nelson AC, Cutty SJ, Niini M, Stemple DL, Flicek P, Houart C, Bruce AEE, Wardle FC. 2014. Global identification of smad2 and eomesodermin targets in zebrafish identifies a conserved transcriptional network in mesendoderm and a novel role for eomesodermin in repression of ectodermal gene expression. BMC Biol 12: 1–20.
	\bibitem[]{citation128} Nepal C, Hadzhiev Y, Previti C, Haberle V, Li N, Takahashi H, Suzuki AMM, Sheng Y, Abdelhamid RF, Anand S, et al. 2013. Dynamic regulation of the transcription initiation landscape at single nucleotide resolution during vertebrate embryogenesis. Genome Res 23: 1938–1950.
	\bibitem[]{citation129} Nobrega MA, Ovcharenko I, Afzal V, Rubin EM. 2003. Scanning human gene deserts for long-range enhancers. Science 302: 413. http://www.sciencemag.org/cgi/doi/10.1126/science.1088328.
	\bibitem[]{citation130} Nora EP, Goloborodko A, Valton AL, Gibcus JH, Uebersohn A, Abdennur N, Dekker J, Mirny LA, Bruneau BG. 2017. Targeted Degradation of CTCF Decouples Local Insulation of Chromosome Domains from Genomic Compartmentalization. Cell 169: 930–944.e22.
	\bibitem[]{citation131} Nora EP, Lajoie BR, Schulz EG, Giorgetti L, Okamoto I, Servant N, Piolot T, Van Berkum NL, Meisig J, Sedat J, et al. 2012. Spatial partitioning of the regulatory landscape of the X-inactivation centre. Nature 485: 381–385.
	\bibitem[]{citation132} Nord AS, Blow MJ, Attanasio C, Akiyama JA, Holt A, Hosseini R, Phouanenavong S, Plajzer-Frick I, Shoukry M, Afzal V, et al. 2013. Rapid and pervasive changes in genome-wide enhancer usage during mammalian development. Cell 155: 1521–1531. http://dx.doi.org/10.1016/j.cell.2013.11.033.
	\bibitem[]{citation133} Novo CL, Javierre B-M, Cairns J, Segonds-Pichon A, Wingett SW, Freire-Pritchett P, Furlan-Magaril M, Schoenfelder S, Fraser P, Rugg-Gunn PJ. 2018. Long-Range Enhancer Interactions Are Prevalent in Mouse Embryonic Stem Cells and Are Reorganized upon Pluripotent State Transition. Cell Rep 22: 2615–2627. http://linkinghub.elsevier.com/retrieve/pii/S2211124718302213.
	\bibitem[]{citation134} Oehler S, Eismann ER, Krämer H, Müller-Hill B. 1990. The three operators of the lac operon cooperate in repression. EMBO J 9: 973–979.
	\bibitem[]{citation135} Paralkar VR, Taborda CC, Huang P, Yao Y, Kossenkov A V., Prasad R, Luan J, Davies JOJ, Hughes JR, Hardison RC, et al. 2016. Unlinking an lncRNA from Its Associated cis Element. Mol Cell 62: 104–110. http://dx.doi.org/10.1016/j.molcel.2016.02.029.
	\bibitem[]{citation136} Pardee AB, Jacob F, Monod J. 1958 [The role of the inducible alleles and the constrtutive alleles in the synthesis of beta-galactosidase in zygotes of Escherichia coli]. C R Hebd Seances Acad Sci. 246: 3125-8. French.
	\bibitem[]{citation137} Pauli A, Valen E, Lin MF, Garber M, Vastenhouw NL, Levin JZ, Fan L, Sandelin A, Rinn JL, Regev A, et al. 2012. Systematic identification of long noncoding RNAs expressed during zebrafish embryogenesis. Genome Res 22: 577–591. http://genome.cshlp.org/cgi/doi/10.1101/gr.133009.111.
	\bibitem[]{citation138} Pennacchio LA, Ahituv N, Moses AM, Prabhakar S, Nobrega MA, Shoukry M, Minovitsky S, Dubchak I, Holt A, Lewis KD, et al. 2006. In vivo enhancer analysis of human conserved non-coding sequences. Nature 444: 499–502.
	\bibitem[]{citation139} Pérez-Rico YA, Boeva V, Mallory AC, Bitetti A, Majello S, Barillot E, Shkumatava A. 2017. Comparative analyses of super-enhancers reveal conserved elements in vertebrate genomes. Genome Res 27: 259–268.
	\bibitem[]{citation140} Pugacheva EM, Kwon YW, Hukriede NA, Pack S, Flanagan PT, Ahn JC, Park JA, Choi KS, Kim KW, Loukinov D, et al. 2006. Cloning and characterization of zebrafish CTCF: Developmental expression patterns, regulation of the promoter region, and evolutionary aspects of gene organization. Gene 375: 26–36.
	\bibitem[]{citation141} Quillien A, Abdalla M, Yu J, Ou J, Zhu LJ, Lawson ND. 2017. Robust Identification of Developmentally Active Endothelial Enhancers in Zebrafish Using FANS-Assisted ATAC-Seq. Cell Rep 20: 709–720. http://dx.doi.org/10.1016/j.celrep.2017.06.070.
	\bibitem[]{citation142} Quinodoz SA, Ollikainen N, Tabak B, Palla A, Schmidt JM, Detmar E, Lai MM, Shishkin AA, Bhat P, Takei Y, et al. 2018. Higher-Order Inter-chromosomal Hubs Shape 3D Genome Organization in the Nucleus. Cell 174: 744–757.e24. https://doi.org/10.1016/j.cell.2018.05.024.
	\bibitem[]{citation143} Rada-Iglesias A, Bajpai R, Swigut T, Brugmann SA, Flynn RA, Wysocka J. 2011. A unique chromatin signature uncovers early developmental enhancers in humans. Nature 470: 279–285. http://dx.doi.org/10.1038/nature09692.
	\bibitem[]{citation144} Rao SSP, Huang SC, Glenn St Hilaire B, Engreitz JM, Perez EM, Kieffer-Kwon KR, Sanborn AL, Johnstone SE, Bascom GD, Bochkov ID, et al. 2017. Cohesin Loss Eliminates All Loop Domains. Cell 171: 305–320.e24. https://doi.org/10.1016/j.cell.2017.09.026.
	\bibitem[]{citation145} Rao SSP, Huntley MH, Durand NC, Stamenova EK, Bochkov ID, Robinson JT, Sanborn AL, Machol I, Omer AD, Lander ES, et al. 2014. A 3D map of the human genome at kilobase resolution reveals principles of chromatin looping. Cell 159: 1665–1680. http://dx.doi.org/10.1016/j.cell.2014.11.021.
	\bibitem[]{citation146} Rastegar S, Hess I, Dickmeis T, Nicod JC, Ertzer R, Hadzhiev Y, Thies WG, Scherer G, Strähle U. 2008. The words of the regulatory code are arranged in a variable manner in highly conserved enhancers. Dev Biol 318: 366–377.
	\bibitem[]{citation147} Ren G, Jin W, Cui K, Rodrigez J, Hu G, Zhang Z, Larson DR, Zhao K. 2017. CTCF-Mediated Enhancer-Promoter Interaction Is a Critical Regulator of Cell-to-Cell Variation of Gene Expression. Mol Cell 67: 1049–1058.e6. http://dx.doi.org/10.1016/j.molcel.2017.08.026.
	\bibitem[]{citation148} Rhee HS, Pugh BF. 2011. Comprehensive genome-wide protein-DNA interactions detected at single-nucleotide resolution. Cell 147: 1408–1419. http://dx.doi.org/10.1016/j.cell.2011.11.013.
	\bibitem[]{citation149} Rhodes JM, Bentley FK, Print CG, Dorsett D, Misulovin Z, Dickinson EJ, Crosier KE, Crosier PS, Horsfield JA. 2010. Positive regulation of c-Myc by cohesin is direct, and evolutionarily conserved. Dev Biol 344: 637–649.
	\bibitem[]{citation150} Roeder RG. 2005. Transcriptional regulation and the role of diverse coactivators in animal cells. FEBS Lett 579: 909–915.
	\bibitem[]{citation151} Rothschild G, Basu U. 2017. Lingering Questions about Enhancer RNA and Enhancer Transcription-Coupled Genomic Instability. Trends Genet 33: 143–154. http://dx.doi.org/10.1016/j.tig.2016.12.002.
	\bibitem[]{citation152} Rowley MJ, Nichols MH, Lyu X, Ando-Kuri M, Rivera ISM, Hermetz K, Wang P, Ruan Y, Corces VG. 2017. Evolutionarily Conserved Principles Predict 3D Chromatin Organization. Mol Cell 67: 837–852.e7. http://dx.doi.org/10.1016/j.molcel.2017.07.022.
	\bibitem[]{citation153} Ruiz-Velasco M, Kumar M, Lai MC, Bhat P, Solis-Pinson AB, Reyes A, Kleinsorg S, Noh KM, Gibson TJ, Zaugg JB. 2017. CTCF-Mediated Chromatin Loops between Promoter and Gene Body Regulate Alternative Splicing across Individuals. Cell Syst 5: 628–637.e6. https://doi.org/10.1016/j.cels.2017.10.018.
	\bibitem[]{citation154} Sabari BR, Agnese AD, Boija A, Klein IA, Coffey L, Shrinivas K, Abraham BJ, Hannett NM, Zamudio A V, Manteiga JC, et al. 2018. Coactivator condensation at super - enhancers links phase separation and gene control. Science 3958: eaar3958. http://www.ncbi.nlm.nih.gov/pubmed/29930091.
	\bibitem[]{citation155} Saint-André V, Federation AJ, Lin CY, Abraham BJ, Reddy J, Lee TI, Bradner JE, Young RA. 2016. Models of human core transcriptional regulatory circuitries. Genome Res 26: 385–396.
	\bibitem[]{citation156} Sanborn AL, Rao SSP, Huang S-C, Durand NC, Huntley MH, Jewett AI, Bochkov ID, Chinnappan D, Cutkosky A, Li J, et al. 2015. Chromatin extrusion explains key features of loop and domain formation in wild-type and engineered genomes. Proc Natl Acad Sci 112: E6456–E6465. http://www.pnas.org/lookup/doi/10.1073/pnas.1518552112.
	\bibitem[]{citation157} Sanyal A, Lajoie BR, Jain G, Dekker J. 2012. The long-range interaction landscape of gene promoters. Nature 489: 109–113. http://dx.doi.org/10.1038/nature11279.
	\bibitem[]{citation157b} Razin SV, Ulianov SV. 2017. Gene functioning and storage within a folded genome. Cellular \& Molecular Biology Letters. 22: 18. doi:10.1186/s11658-017-0050-4.
	\bibitem[]{citation158} Schaffner W. 2015. Enhancers, enhancers - From their discovery to today’s universe of transcription enhancers. Biol Chem 396: 311–327.
	\bibitem[]{citation159} Schikora-Tamarit MÀ, Lopez-Grado i Salinas G, Gonzalez-Navasa C, Calderón I, Marcos-Fa X, Sas M, Carey LB. 2018. Promoter Activity Buffering Reduces the Fitness Cost of Misregulation. Cell Rep 24: 755–765. http://www.ncbi.nlm.nih.gov/pubmed/30021171.
	\bibitem[]{citation160} Schmidt D, Schwalie PC, Wilson MD, Ballester B, Gonalves Â, Kutter C, Brown GD, Marshall A, Flicek P, Odom DT. 2012. Waves of retrotransposon expansion remodel genome organization and CTCF binding in multiple mammalian lineages. Cell 148: 335–348.
	\bibitem[]{citation161} Schmitt AD, Hu M, Jung I, Xu Z, Qiu Y, Tan CL, Li Y, Lin S, Lin Y, Barr CL, et al. 2016. A Compendium of Chromatin Contact Maps Reveals Spatially Active Regions in the Human Genome. Cell Rep 17: 2042–2059. http://dx.doi.org/10.1016/j.celrep.2016.10.061.
	\bibitem[]{citation162} Schwarzer W, Abdennur N, Goloborodko A, Pekowska A, Fudenberg G, Loe-Mie Y, Fonseca NA, Huber W, Haering CH, Mirny L, et al. 2017. Two independent modes of chromatin organization revealed by cohesin removal. Nature 551: 51–56. http://dx.doi.org/10.1038/nature24281.
	\bibitem[]{citation163} Sebé-Pedrós A, Ballaré C, Parra-Acero H, Chiva C, Tena JJ, Sabidó E, Gómez-Skarmeta JL, Di Croce L, Ruiz-Trillo I. 2016. The Dynamic Regulatory Genome of Capsaspora and the Origin of Animal Multicellularity. Cell 165: 1224–1237.
	\bibitem[]{citation164} Servant N, Varoquaux N, Lajoie BR, Viara E, Chen C-J, Vert J-P, Heard E, Dekker J, Barillot E. 2015. HiC-Pro: an optimized and flexible pipeline for Hi-C data processing. Genome Biol 16: 259. http://genomebiology.com/2015/16/1/259.
	\bibitem[]{citation165} Sexton T, Yaffe E, Kenigsberg E, Bantignies F, Leblanc B, Hoichman M, Parrinello H, Tanay A, Cavalli G. 2012. Three-dimensional folding and functional organization principles of the Drosophila genome. Cell 148: 458–472.
	\bibitem[]{citation166} Shen Y, Yue F, Mccleary DF, Ye Z, Edsall L, Kuan S, Wagner U, Dixon J, Lee L, Lobanenkov V V, et al. 2012. genome. Nature 488: 116–120. http://dx.doi.org/10.1038/nature11243.
	\bibitem[]{citation167} Shin HY, Willi M, Yoo KH, Zeng X, Wang C, Metser G, Hennighausen L. 2016. Hierarchy within the mammary STAT5-driven Wap super-enhancer. Nat Genet 48: 904–911. http://dx.doi.org/10.1038/ng.3606.
	\bibitem[]{citation168} Shlyueva D, Stampfel G, Stark A. 2014. Transcriptional enhancers: From properties to genome-wide predictions. Nat Rev Genet 15: 272–286. http://dx.doi.org/10.1038/nrg3682.
	\bibitem[]{citation169} Shukla S, Kavak E, Gregory M, Imashimizu M, Shutinoski B, Kashlev M, Oberdoerffer P, Sandberg R, Oberdoerffer S. 2011. CTCF-promoted RNA polymerase II pausing links DNA methylation to splicing. Nature 479: 74–79. http://dx.doi.org/10.1038/nature10442.
	\bibitem[]{citation170} Siersbæk R, Rabiee A, Nielsen R, Sidoli S, Traynor S, Loft A, Poulsen LLC, Rogowska-Wrzesinska A, Jensen ON, Mandrup S. 2014. Transcription factor cooperativity in early adipogenic hotspots and super-enhancers. Cell Rep 7: 1443–1455. http://dx.doi.org/10.1016/j.celrep.2014.04.042.
	\bibitem[]{citation171} Strom AR, Emelyanov A V., Mir M, Fyodorov D V., Darzacq X, Karpen GH. 2017. Phase separation drives heterochromatin domain formation. Nature 547: 241–245. http://dx.doi.org/10.1038/nature22989.
	\bibitem[]{citation172} Suzuki HI, Young RA, Sharp PA. 2017. Super-Enhancer-Mediated RNA Processing Revealed by Integrative MicroRNA Network Analysis. Cell 168: 1000–1014.e15. http://dx.doi.org/10.1016/j.cell.2017.02.015.
	\bibitem[]{citation173} Symmons O, Pan L, Remeseiro S, Aktas T, Klein F, Huber W, Spitz F. 2016. The Shh Topological Domain Facilitates the Action of Remote Enhancers by Reducing the Effects of Genomic Distances. Dev Cell 39: 529–543.
	\bibitem[]{citation174} Taher L, McGaughey DM, Maragh S, Aneas I, Bessling SL, Miller W, Nobrega MA, McCallion AS, Ovcharenko I. 2011. Genome-wide identification of conserved regulatory function in diverged sequences. Genome Res 21: 1139–1149. http://genome.cshlp.org/cgi/doi/10.1101/gr.119016.110.
	\bibitem[]{citation175} Tan JY, Smith AAT, Ferreira da Silva M, Matthey-Doret C, Rueedi R, Sönmez R, Ding D, Kutalik Z, Bergmann S, Marques AC. 2017. cis-Acting Complex-Trait-Associated lincRNA Expression Correlates with Modulation of Chromosomal Architecture. Cell Rep 18: 2280–2288.
	\bibitem[]{citation176} Tang Z, Luo OJ, Li X, Zheng M, Zhu JJ, Szalaj P, Trzaskoma P, Magalska A, Wlodarczyk J, Ruszczycki B, et al. 2015. CTCF-Mediated Human 3D Genome Architecture Reveals Chromatin Topology for Transcription. Cell 163: 1611–1627. http://dx.doi.org/10.1016/j.cell.2015.11.024.
	\bibitem[]{citation177} Tena JJ, Alonso ME, de la Calle-Mustienes E, Splinter E, de Laat W, Manzanares M, Gómez-Skarmeta JL. 2011. An evolutionarily conserved three-dimensional structure in the vertebrate Irx clusters facilitates enhancer sharing and coregulation. Nat Commun 2: 310. http://www.nature.com/articles/ncomms1301.
	\bibitem[]{citation178} Tran Mau-Them F, Guibaud L, Duplomb L, Keren B, Lindstrom K, Marey I, Mochel F, van den Boogaard MJ, Oegema R, Nava C, et al. 2018. De novo truncating variants in the intronless IRF2BPL are responsible for developmental epileptic encephalopathy. Genet Med Aug 31. doi: 10.1038/s41436-018-0143-0. http://www.ncbi.nlm.nih.gov/pubmed/30166628.
	\bibitem[]{citation179} Ulianov S V., Khrameeva EE, Gavrilov AA, Flyamer IM, Kos P, Mikhaleva EA, Penin AA, Logacheva MD, Imakaev M V., Chertovich A, et al. 2016. Active chromatin and transcription play a key role in chromosome partitioning into topologically associating domains. Genome Res 26: 70–84. http://genome.cshlp.org/content/26/1/70.full.pdf.
	\bibitem[]{citation180} Vahedi G, Kanno Y, Furumoto Y, Jiang K, Parker SCJ, Erdos MR, Davis SR, Roychoudhuri R, Restifo NP, Gadina M, et al. 2015. Super-enhancers delineate disease-associated regulatory nodes in T cells. Nature 520: 558–562.
	\bibitem[]{citation181} Valouev A, Johnson SM, Boyd SD, Smith CL, Fire AZ, Sidow A. 2011. Determinants of nucleosome organization in primary human cells. Nature 474: 516–522. http://dx.doi.org/10.1038/nature10002.
	\bibitem[]{citation182} Van Bortle K, Ramos E, Takenaka N, Yang J, Wahi JE, Corces VG. 2012. Drosophila CTCF tandemly aligns with other insulator proteins at the borders of H3K27me3 domains. Genome Res 22: 2176–2187.
	\bibitem[]{citation183} Vanhille L, Griffon A, Maqbool MA, Zacarias-Cabeza J, Dao LTM, Fernandez N, Ballester B, Andrau JC, Spicuglia S. 2015. High-throughput and quantitative assessment of enhancer activity in mammals by CapStarr-seq. Nat Commun 6: 6905. http://www.nature.com/articles/ncomms7905.
	\bibitem[]{citation184} Vastenhouw NL, Zhang Y, Woods IG, Imam F, Regev A, Liu XS, Rinn J, Schier AF. 2010. Chromatin signature of embryonic pluripotency is established during genome activation. Nature 464: 922–926. http://dx.doi.org/10.1038/nature08866.
	\bibitem[]{citation185} Vermunt MW, Reinink P, Korving J, de Bruijn E, Creyghton PM, Basak O, Geeven G, Toonen PW, Lansu N, Meunier C, et al. 2014. Large-scale identification of coregulated enhancer networks in the adult human brain. Cell Rep 9: 767–779.
	\bibitem[]{citation186} Vesterlund L, Jiao H, Unneberg P, Hovatta O, Kere J. 2011. The zebrafish transcriptome during early development. BMC Dev Biol 11: 30. http://www.biomedcentral.com/1471-213X/11/30.
	\bibitem[]{citation187} Vian L, Pekowska A, Rao SS, Kieffer-Kwon K-R, Jung S, Baranello L, Huang S-C, El Khattabi L, Dose M, Pruett N, et al. 2018. The Energetics and Physiological Impact of Cohesin Extrusion. Cell 173: 1165–1178.e20. https://doi.org/10.1016/j.cell.2018.03.072.
	\bibitem[]{citation188} Vietri Rudan M, Barrington C, Henderson S, Ernst C, Odom DT, Tanay A, Hadjur S. 2015. Comparative Hi-C Reveals that CTCF Underlies Evolution of Chromosomal Domain Architecture. Cell Rep 10: 1297–1309. http://dx.doi.org/10.1016/j.celrep.2015.02.004.
	\bibitem[]{citation189} Villar D, Berthelot C, Flicek P, Odom DT, Villar D, Berthelot C, Aldridge S, Rayner TF, Lukk M, Pignatelli M. 2015. Enhancer Evolution across 20 Mammalian Species Article Enhancer Evolution across 20 Mammalian Species. Cell 160: 554–566. http://dx.doi.org/10.1016/j.cell.2015.01.006.
	\bibitem[]{citation190} Visel A, Blow MJ, Li Z, Zhang T, Akiyama JA, Holt A, Plajzer-Frick I, Shoukry M, Wright C, Chen F, et al. 2009. ChIP-seq accurately predicts tissue-specific activity of enhancers. Nature 457: 854–858. http://dx.doi.org/10.1038/nature07730.
	\bibitem[]{citation191} Wagner DE, Weinreb C, Collins ZM, Briggs JA, Megason SG, Klein AM. 2018. Single-cell mapping of gene expression landscapes and lineage in the zebrafish embryo. Science (80- ) 360: 981–987. http://www.sciencemag.org/lookup/doi/10.1126/science.aar4362.
	\bibitem[]{citation192} Weingarten-Gabbay S, Segal E. 2014. A shared architecture for promoters and enhancers. Nat Genet 46: 1253–1254.
	\bibitem[]{citation193} White RJ, Collins JE, Sealy IM, Wali N, Dooley CM, Digby Z, Stemple DL, Murphy DN, Billis K, Hourlier T, et al. 2017. A high-resolution mRNA expression time course of embryonic development in zebrafish. Elife 6: 1–32. https://elifesciences.org/articles/30860.
	\bibitem[]{citation194} Whyte WA, Orlando DA, Hnisz D, Abraham BJ, Lin CY, Kagey MH, Rahl PB, Lee TI, Young RA. 2013. Master transcription factors and mediator establish super-enhancers at key cell identity genes. Cell 153: 307–319. http://dx.doi.org/10.1016/j.cell.2013.03.035.
	\bibitem[]{citation195} Wittkopp PJ, Kalay G. 2012. Cis-regulatory elements: Molecular mechanisms and evolutionary processes underlying divergence. Nat Rev Genet 13: 59–69. http://dx.doi.org/10.1038/nrg3095.
	\bibitem[]{citation196} Woolfe A, Goodson M, Goode DK, Snell P, McEwen GK, Vavouri T, Smith SF, North P, Callaway H, Kelly K, et al. 2004. Highly Conserved Non-Coding Sequences Are Associated with Vertebrate Development ed. Sean Eddy. PLoS Biol 3: e7. http://dx.plos.org/10.1371/journal.pbio.0030007.
	\bibitem[]{citation197} Wutz G, Várnai C, Nagasaka K, Cisneros DA, Stocsits RR, Tang W, Schoenfelder S, Jessberger G, Muhar M, Hossain MJ, et al. 2017. Topologically associating domains and chromatin loops depend on cohesin and are regulated by CTCF, WAPL, and PDS5 proteins. EMBO J 36: e201798004. http://emboj.embopress.org/lookup/doi/10.15252/embj.201798004.
	\bibitem[]{citation198} Xu C, Fan ZP, Müller P, Fogley R, DiBiase A, Trompouki E, Unternaehrer J, Xiong F, Torregroza I, Evans T, et al. 2012. Nanog-like Regulates Endoderm Formation through the Mxtx2-Nodal Pathway. Dev Cell 22: 625–638.
	\bibitem[]{citation199} Zhan Y, Mariani L, Barozzi I, Schulz EG, Blüthgen N, Stadler M, Tiana G, Giorgetti L. 2017. Reciprocal insulation analysis of Hi-C data shows that TADs represent a functionally but not structurally privileged scale in the hierarchical folding of chromosomes. Genome Res 27: 479–490.
	\bibitem[]{citation200} Zhang Y, Vastenhouw NL, Feng J, Fu K, Wang C, Ge Y, Pauli A, Van Hummelen P, Schier AF, Liu XS. 2014. Canonical nucleosome organization at promoters forms during genome activation. Genome Res 24: 260–266.
	\bibitem[]{citation201} Zhou H, Schmidt SCS, Jiang S, Willox B, Bernhardt K, Liang J, Johannsen EC, Kharchenko P, Gewurz BE, Kieff E, et al. 2015. Epstein-barr virus oncoprotein super-enhancers control B cell growth. Cell Host Microbe 17: 205–216. http://dx.doi.org/10.1016/j.chom.2014.12.013.

\end{thebibliography}



